manuscript - APP

### 2018-10-16 R/manuscript_app.Rmd
compute average accuracy for speed differences
polish code for review

---
title: "manuscript - APP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

@@

```{r Figure 1}
traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

@@

ggsave(file.path(plot_pth, "Figure1_ballistic.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure1_brownian.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure1_ballistic.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure1_brownian.eps"), p2, width = 6, height = 6)
```

```{r Figure 2}

p1 <- plot_fig2(4, "Brownian-like-distractors")
p2 <- plot_fig2(16, "Ballistic-like-distractors")

@@

ggsave(file.path(plot_pth, "Figure2_brownian.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p2, width = 6, height = 6)
```

@@

## Figure 3a

```{r}
p_k2 <- plot_fig3(2)
p_k4 <- plot_fig3(4)
p_k8 <- plot_fig3(8)
p_k16 <- plot_fig3(16)
p_k64 <- plot_fig3(64)
p_k64_legend <- plot_fig3(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

## Figure 3b

```{r Figure 3b}
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
  ungroup()
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

# duplicated values for contrast 0
accu_summaryx <- bind_rows(
  accu_summary,
  accu_summary %>% 
    filter(contrast_abs == 0, target_straight == F) %>% 
    mutate(target_straight = T)
)

p <- accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
  theme(aspect.ratio = 1) + 
  scale_shape_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  scale_linetype_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  xlab("contrast") + ylab("Accuracy")
p
ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)
```

@@

```{r exp 1b - compute the assymetry, warning=F}
df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))

@@

```{r exp1b - test vs baseline}
df_exp1b %>% 
  group_by(type, restk, subject) %>% 
  summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>%
  filter(accuracy < 1) %>% 
  do(t.test(.$accuracy, mu = .125) %>% 
       broom::tidy()) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  knitr::kable()
```

```{r exp 1b - Table 1}
df_exp1b %>% 
  filter(restk == 2) %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp1b %>% 
  filter(restk == 4) %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()
df_exp1b %>% 
  filter(restk == 8) %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp1b %>% 
  filter(restk == 16) %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

@@

```{r exp 2a - overall differences, warning=F, message = F}
df_exp2a %>% 
  filter(restk2 == "Slow-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = as.type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp2a %>% 
  filter(restk2 == "Fast-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = as.factor(subject),
        within = as.factor(type), 
        detailed = T) %>% 
  apa::anova_apa()

@@

### Figure 4

```{r Figure 4}

p1 <- plot_fig4(2, ggtit = "Slow-moving-distractors")

p2 <- plot_fig4(4, ggtit = "Fast-moving-distractors")

@@

ggsave(file.path(plot_pth, "Figure4_slow.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure4_fast.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure4_slow.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure4_fast.eps"), p2, width = 6, height = 6)
```

@@

df2_exp2b <- rbind(df_exp2b, df_exp2b)
df2_exp2b$version <- 2
df2_exp2b$version[1:nrow(df_exp2b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp2b$restk
df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
df2_exp2b$type[df2_exp2b$version == 2] <- tmp

df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
```

@@

p_sp05 <- plot_fig5(0.5)
p_sp1 <- plot_fig5(1)
p_sp2 <- plot_fig5(2)
p_sp4 <- plot_fig5(4)
p_sp8 <- plot_fig5(8)
p_sp8_legend <- plot_fig5(8, show_legend = T)

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
ggsave(file.path(plot_pth, "Fig5_sp05.eps"), p_sp05, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp1.eps"), p_sp1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp2.eps"), p_sp2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp4.eps"), p_sp4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp8.eps"), p_sp8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp8_legend.eps"), p_sp8_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

```{r exp 2b - compute the assymetry, warning=F}
df3_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(p=compute.p(.))

>>>>

---
title: "manuscript - APP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  word_document: default
  html_document: default
---

@@

Created by script *generate_vonmises_example*

```{r Figure 2}
traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

@@

ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_brownian.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p2, width = 6, height = 6)
```

## Figure 3

```{r Figure 3}

p1 <- plot_fig3(4, "Brownian-like-distractors")
p2 <- plot_fig3(16, "Ballistic-like-distractors")

@@

ggsave(file.path(plot_pth, "Figure3_brownian.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure3_ballistic.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure3_brownian.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure3_ballistic.eps"), p2, width = 6, height = 6)
```

@@

## Figure 4

```{r Figure 4}
p_k2 <- plot_fig4(2)
p_k4 <- plot_fig4(4)
p_k8 <- plot_fig4(8)
p_k16 <- plot_fig4(16)
p_k64 <- plot_fig4(64)
p_k64_legend <- plot_fig4(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
ggsave(file.path(plot_pth, "Fig4_k2.eps"), p_k2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig4_k4.eps"), p_k4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig4_k8.eps"), p_k8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig4_k16.eps"), p_k16, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig4_k64.eps"), p_k64, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig4_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

p <- plot_fig5()
ggsave(file.path(plot_pth, "Figure5.png"), p, width = 9, height = 6)
```

```{r Table 1, warning=F, message=F}
df_exp1b %>% 
  filter(contrast_abs > 0) %>% 
  group_by(contrast_abs) %>% 
  do(ez::ezANOVA(data = ., dv = accuracy, within = .(target_straight), wid = id)$ANOVA) %>% 
  ungroup() %>% 
  transmute(`Contrast level` = contrast_abs, `F(1,16)` = F, p = round(p, 3), ges = round(ges,2)) %>% 
  knitr::kable(caption = "Results of within-subject ANCOVAs for each contrast level for movement variability")
```

@@

```{r exp 1b - compute the assymetry, warning=F,eval = FALSE}
df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))

@@

```{r exp1b - test vs baseline}
df_exp1b %>% 
  group_by(targetk, restk, subject) %>% 
  summarize(accuracy = mean(accuracy)) %>% group_by(restk, targetk) %>%
  filter(accuracy < 1) %>% 
  do(t.test(.$accuracy, mu = .125) %>% 
       broom::tidy()) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  knitr::kable()
```

@@

```{r exp 2a - overall differences, warning=F, message = F}
df_exp2a %>% 
  filter(restk2 == "Slow-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = as.factor(subject),
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp2a %>% 
  filter(restk2 == "Fast-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = as.factor(subject),
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

@@

### Figure 6

```{r Figure 6}

p1 <- plot_fig6(2, ggtit = "Slow-moving-distractors")

p2 <- plot_fig6(4, ggtit = "Fast-moving-distractors")

@@

ggsave(file.path(plot_pth, "Figure6_slow.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure6_fast.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure6_slow.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure6_fast.eps"), p2, width = 6, height = 6)
```

@@

@@

## Descriptive statistics

```{r accuracy for speed differences }

df_exp2b %>% filter(abs(targetspd-restspd) >= 1) %>% summarize(m = mean(accuracy), sd = sd(accuracy)) %>% knitr::kable(digits = 2)

df_exp2b %>% filter(contrast_abs >= 2, target_faster== F) %>% summarize(m = mean(accuracy), sd = sd(accuracy)) %>% knitr::kable(digits = 2)

## Figure 7

```{r Figure 7}

p_sp05 <- plot_fig7(0.5)
p_sp1 <- plot_fig7(1)
p_sp2 <- plot_fig7(2)
p_sp4 <- plot_fig7(4)
p_sp8 <- plot_fig7(8)
#p_sp8_legend <- plot_fig5(8, show_legend = T)

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
ggsave(file.path(plot_pth, "Fig7_sp05.eps"), p_sp05, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig7_sp1.eps"), p_sp1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig7_sp2.eps"), p_sp2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig7_sp4.eps"), p_sp4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig7_sp8.eps"), p_sp8, width = 6, height = 6)

# final plot was created in inkscape
```

## Figure 8

```{r}

p <- plot_fig8()
ggsave(file.path(plot_pth, "Figure8.png"), p, width = 9, height = 6)

## Table 2

```{r exp2b - Table 2}
df_exp2b %>% 
  filter(contrast_abs > 0) %>% 
  group_by(contrast_abs) %>% 
  do(ez::ezANOVA(data = ., dv = accuracy, within = .(target_faster), wid = id)$ANOVA) %>% 
  ungroup() %>% 
  transmute(`Contrast level` = contrast_abs, `F(1,15)` = F, p = round(p, 3), ges = round(ges,2)) %>% 
  knitr::kable()

@@

```{r exp 2b - compute the assymetry, warning=F,eval = FALSE}
df3_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(p=compute.p(.))
